\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{PRIYANK RAI} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{(+91)7898099570 \\ Bhopal, Madhya Pradesh, India \\ \* 4 October, 2000.
 } 
\address{\href{mailto:priyankraiiiii@gmail.com}{priyankraiiiii@gmail.com} \\ \href{https://linkedin.com/in/urstrulypriyank}{linkedin} \\ \href{www.priyankrai.live}{www.priyankrai.live} \\ 
\href{https://github.com/urstrulypriyank/}{github} \\
}
%
\begin{document}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Lakshmi Narain College of Technology \& Science, Bhopal} \hfill {\em July 2019 - May 2023} 
\\ Bachelor of Technology, Computer Science and Engineering.\hfill { Overall CGPA: 8.03 }



%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}


%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Recent computer science graduate with strong programming skills and a passion for developing innovative software solutions. Seeking a software developer role where I can utilize my knowledge of programming languages and software development methodologies to contribute to the success of a dynamic and forward-thinking company.}


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL SKILLS	
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & C, C++,JAVA Python3, Javascript, BASH  \\
Frameworks and Libraries & React, Node.js, Express, Next.js, Redux, \\
Markup Languages & HTML5, CSS3, YAML\\
Tools & Linux, Docker, Kubernetes, Git, \\
Databases & MySql, Sqlite, MongoDB\\
Cloud Services & AWS S3 ,EC2 , VPC\\
\end{tabular}

\end{rSection}



% \begin{rSection}{EXPERIENCE}

% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}
 
% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}

% \end{rSection} 


\begin{rSection}{Work Experience}
\begin{rSubsection}{Cisco Networking Academy, India}{April 2021 - Jun 2021}{Cybersecurity Intern}{}
 \item Analysed the network security.
 \item Design and analyzed the network in packet tracer network simulation.
 \item Explored Linux and tools like Wireshark, dig etc.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Video conferencing application .} {It is a full stack web conferencing solution built using javascript HTML and CSS and supports autoscaling via Kubernetes, Functionality include Voice broadcasting, Screen Sharing, Video conferencing etc. }
\item \textbf{Notes sharing application .} {Build a project that supports sharing and storing notes, It is a web application built using MERN stack, It has authentication session management and notes sync to cloud storing in MongoDB parsed as JSON  .}
\item \textbf{Chess game.} {It is a multiplayer chess game built using python3 with the help of pygame. It does follow all the rules of real chess game functionality include piece movement, check ,check mate, game restart etc..\href{https://github.com/urstrulypriyank/chess_markv1/}{(Try it here)}}
\end{rSection} 




%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{certifications}
{\bf NDG LINUX ESSENTIAL} \hfill {\em July 2021 - Present} 
\\ {cisco networking academy} 
\\
{\bf TECHNICAL SUPPORT FUNDAMENTAL} \hfill {\em April 2020 - Present} 
\\offered by google through Coursera.
\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\begin{rSection}{Languages \& Other Interests } 

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
English \ & Full Professional Proficiency  \\
Hindi \ & Native or Bilingual Proficiency  \\
Hobby \ & Desktop Ricing, Devops, Traveling, Chess
\end{tabular}
\end{rSection}


\end{document}
